Towards the Internet of Things: A Real-World Testbed

### 2013-06-24 trunk/doc/paper- towards the internet of things/paper v1.tex
THESIS DIR ADDED WITH AN INITIAL OUTLINE OF THE REPORT

\title{Towards the Internet of Things: A Real-World Testbed}
\author{\IEEEauthorblockN{Nacer Khalil}
\IEEEauthorblockA{School of Electrical and Engineering\\
Al Akhawayn University In Ifrane\\
Email: n.khalil@aui.ma}
\and
\IEEEauthorblockN{Mohamed Riduan Abid}
\IEEEauthorblockA{School of Electrical and Engineering\\
Al Akhawayn University In Ifrane\\
Email: r.abid@aui.ma}
\and
\IEEEauthorblockN{Driss Benhaddou}
\IEEEauthorblockA{School of Engineering and Technology\\
University of Houston\\
Email: dbenhaddou@uh.edu}}
\maketitle
\begin{abstract}
The internet has seen its importance grow exponentially throughout the previous two decades. It has started as set of computers sharing static information written by human beings and accessed by other human beings. It followed mainly the publisher subscriber model. Later on, with the arrival of internet 2.0, the subscriber had now the ability to affect the content at the publisher's level and this basic idea gave rise to a whole new world of applications such as wikis, blogs, social networks and other applications. The next revolution in the internet is the introduction of machines as players within the internet. This will allow the machines to intercommunicate between them or what is known as machine-to-machine communication. More and more devices will be able to communicate and thus be part of the internet. This will give rise to a whole new dimension of possibilities as the focus of the internet will not only be human interactions but also machine interactions. As an example of autonomous machines communicating through, the components of smart grids will be part of the internet of things. Devices such as AMI, smart homes, wireless sensor networks will all be part of the internet of things. Any device within the smart grid will be uniquely identified through the network and therefore will be able to communicate. In this paper, we present a real-world testbed for integrating wireless sensors into the internet. The solution uses 6lowPAN, and addresses relevant issues at the level of the gateway. we used legacy hardware and proved communication.
\end{abstract}

@@

%\IEEEpeerreviewmaketitle
\section{Introduction}
The direction that is taken by the global society is a direction leading to what is known by "always connected" model. People are eager to receive the information as fast as possible and whenever available. They also want to send information as fast as possible and whenever wanted. Also, these requests and responses that are dictated by the human are not all the time directed towards humans , but can be sent also to devices and machines but that is not always possible at this time being. The future  of internet goes into this direction: being able to connect human beings as well as machine in order to provide robust and flexible communication for all. The machines on the other hand need an interface to be able to communicate on the internet. In this paper, we create a small network where a machine-to-machine communication is possible. This can be part of what is known as internet of things. The testbed created is composed of a wireless sensor network(WSN), a middleware station and a mobile client within the field of smart grids where data is collected from the motes within the WSN and sent to the middleware. The mobile client accesses this data and the mobile client can send messages directly to any mote within the WSN network in order to turn on or off any appliance. The issues that were handled are the following:
\begin{itemize}
\item The system is developed using heterogeneous networks, different data link layer technologies
\item The WSN uses IPV6 over 6lowPAN whereas other components of the system use IPV4
\end{itemize}
To solve these issues, different programs have been used to deal with these issues.

\section{Literature review}

@@

\bibliographystyle{plain}
\bibliography{myrefs}

>>>>

\title{Towards the Internet of Things: A Real-World Testbed}
\author{\IEEEauthorblockN{Nacer Khalil}
\IEEEauthorblockA{School of Electrical and Engineering\\
Al Akhawayn University In Ifrane\\
Email: n.khalil@aui.ma}
\and
\IEEEauthorblockN{Mohamed Riduan Abid}
\IEEEauthorblockA{School of Electrical and Engineering\\
Al Akhawayn University In Ifrane\\
Email: r.abid@aui.ma}
\and
\IEEEauthorblockN{Driss Benhaddou}
\IEEEauthorblockA{School of Engineering and Technology\\
University of Houston\\
Email: dbenhaddou@uh.edu}}
\maketitle
\begin{abstract}
The internet has seen its importance grow exponentially throughout the previous two decades. It has started as a set of computers sharing static information written by human beings and accessed by other human beings. It followed mainly the publisher subscriber model. Later on, with the arrival of internet 2.0, the subscriber had now the ability to affect the content at the publisher's level and this basic idea gave rise to a whole new world of applications such as wikis, blogs, social networks and other applications. The next revolution in the internet is the introduction of machines as players within the internet. This will allow the machines to intercommunicate between them or what is known as machine-to-machine communication. More and more devices will be able to communicate and thus be part of the internet. This will give rise to a whole new dimension of possibilities as the focus of the internet will not only be human interactions but also machine interactions. As an example of autonomous machines communicating through, the components of smart grids will be part of the internet of things. Devices such as AMI, smart homes, wireless sensor networks will all be part of the internet of things. Any device within the smart grid will be uniquely identified through the network and therefore will be able to communicate. In this paper, we present a real-world testbed for integrating wireless sensors into the internet. The solution uses 6lowPAN, and addresses relevant issues at the level of the gateway. we used legacy hardware and proved communication.
\end{abstract}

@@

\section{Introduction}
The direction that is taken by the global society is a direction leading to what is known by "always connected" model. People are eager to receive the information as fast as possible and whenever available. They also want to send information as fast as possible and whenever wanted. Also, these requests and responses that are dictated by the human are not all the time directed towards humans , but can be sent also to devices and machines but that is not always possible at this time being. The future  of internet goes into this direction: being able to connect human beings as well as machine in order to provide robust and flexible communication for all. The machines on the other hand need an interface to be able to communicate on the internet.There will be millions of devices in the internet both producing and consuming information \cite{ref8}. In this paper, we create a small network where a machine-to-machine communication is possible. This can be part of what is known as internet of things \cite{ref6}. The testbed created is composed of a wireless sensor network(WSN), a middleware station and a mobile client within the field of smart grids where data is collected from the motes within the WSN and sent to the middleware. The mobile client accesses this data and the mobile client can send messages directly to any mote within the WSN network in order to turn on or off any appliance. The issues that were handled are the following:
\begin{itemize}
\item The system is developed using heterogeneous networks, different data link layer technologies
\item The WSN uses IPV6 over 6lowPAN whereas other components of the system use IPV4
\end{itemize}
To solve these issues, different programs have been used to deal with these issues.

\section{Literature review}
Smart grid as being one of the most important applications of the internet of things makes use of different technologies such as Zigbee in the WSN \cite{ref1}.  \cite{ref2} discusses the need to introduce IPV6 within the wireless sensor networks and discusses the the existing approaches as well as the issues related to introducing IPV6 on top of Zigbee. Such issues are fragmentation, frame size, addressing, and security issues. This paper introduces a real testbed that includes the whole TCP/IP protocol provided by the BLIP project that takes into consideration most of those issues and implement the two-way communication as needed by smart grids and measures the performance of such a system. El Kouche also investigates on the widely used architectures and technologies and explains which architecture is the most suitable for a WSN within the internet of things \cite{ref3}. \cite{ref4} discusses the requirement of the IOT gateway as well as a proposed architecture for the system to be deployed in the gateway. A rather similar architecture to what is done in this paper is proposed by Yerra, Bharathi, Rajalakshmi and Desai \cite{ref7}. They also use GSM technology to transmit information whereas in our case, internet is used for this purpose.
\

@@

%Bibliography
\mbox{}
\nocite{*}
\bibliographystyle{IEEEtran} 
\bibliography{IEEEabrv,myrefs}
